---
bibliography: ref.bib
output:
  github_document:
    fig_width: 8
    fig_height: 6
    dev: svg
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE, comment = "#>",
    fig.path = "man/figures/README-", out.width = "100%"
)
```

# LearnNonparam

[![R-CMD-check](https://github.com/qddyy/LearnNonparam/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/qddyy/LearnNonparam/actions/workflows/R-CMD-check.yaml)


This package implements most of the tests in chapters 1-5 of [@Higgins2003](#references).

It uses [R6](https://cran.r-project.org/package=R6) for clean OO-design and [arrangements](https://cran.r-project.org/package=arrangements) for fast generation of permutations.

## Installation

You can install the development version of this package with:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("qddyy/LearnNonparam")
```

## Usage

```{r}
library(LearnNonparam)
```

- Create a test (for example, a `Wilcoxon` object)
    ```{r}
    t <- Wilcoxon$new(type = "permu", n_permu = 10000)
    ```

    or you can use `pmt` (**p**er**m**utation **t**est) function (*Recommended*):
    ```{r}
    t <- pmt("twosample.wilcoxon", type = "permu", n_permu = 10000)
    ```

- feed it the data (a data frame, a list, or some numeric vectors)
    ```{r}
    t$feed(Table2.6.2)
    ```

- check the results
    ```{r}
    t$print()

    t$plot(bins = 12)
    ```

- modify some attributes and see how the results change
    ```{r}
    t$type <- "approx"

    print(t$p_value)
    ```

There is also support for chaining method calls, which means that you can do things like

```{r, eval = FALSE}
pmt("twosample.wilcoxon", type = "permu", n_permu = 10000)$feed(Table2.6.2)$print()$plot()
```

## Help

Just use `?...` syntax. 

If you want to know available methods and attributes, you can start by exploring `?PermuTest` (all tests' **base class**). 

If you want to know available tests, see `pmts(...)`. 

```{r}
pmts("twosample")
```

## References