---
bibliography: ref.bib
output:
  github_document:
    df_print: kable
    fig_width: 8
    fig_height: 6
    dev: svg
---

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE, comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)

seed <- 2023
set.seed(seed)
options(pmt_seed = seed)
```

# LearnNonparam

[![GPL license](https://img.shields.io/github/license/qddyy/LearnNonparam)](https://cran.r-project.org/web/licenses/GPL-2)
[![GitHub R package version](https://img.shields.io/github/r-package/v/qddyy/LearnNonparam)](https://github.com/qddyy/LearnNonparam)
[![Code size](https://img.shields.io/github/languages/code-size/qddyy/LearnNonparam.svg)](https://github.com/qddyy/LearnNonparam)
[![CodeFactor](https://www.codefactor.io/repository/github/qddyy/LearnNonparam/badge)](https://www.codefactor.io/repository/github/qddyy/LearnNonparam)
[![R CMD check](https://github.com/qddyy/LearnNonparam/workflows/R-CMD-check/badge.svg)](https://github.com/qddyy/LearnNonparam/actions)

## Overview

This package implements most of the tests in chapters 1-5 of [@Higgins2003](#references).

It uses [R6](https://cran.r-project.org/package=R6) for clean OO-design and [RcppAlgos](https://cran.r-project.org/package=RcppAlgos) for fast generation of combinations/permutations, as well as [ggplot2](https://cran.r-project.org/package=ggplot2) to draw pretty graphs.

Examples in the book can be found [here](https://qddyy.github.io/LearnNonparam/articles/examples). 

## Installation

You can install the development version of this package with:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("qddyy/LearnNonparam")
```

## Usage

```{r}
library(LearnNonparam)
```

- Create a test object (for example, a `Wilcoxon` object)
    ```{r, eval = FALSE}
    t <- Wilcoxon$new(alternative = "greater", type = "permu", n_permu = 1000000)
    ```

    or you can use `pmt` (**p**er**m**utation **t**est) function (*Recommended*):
    ```{r, create}
    t <- pmt("twosample.wilcoxon", alternative = "greater", type = "permu", n_permu = 1000000)
    ```

- feed it the data (a data frame, a list, or numeric vectors)
    ```{r, feed}
    t$feed(rnorm(20, mean = 1), rnorm(20, mean = 0))
    ```

- check the results
    ```{r, results}
    t$p_value

    t$print()

    t$plot(binwidth = 1)
    ```

- modify some attributes and see how the results change
    ```{r, modify}
    t$type <- "approx"

    t$p_value
    ```

There is also support for chaining method calls, which means that you can do things like

```{r, eval = FALSE}
t <- pmt(...)$feed(...)$print(...)$plot(...)
```

## Tips

- Use `options(pmt_seed = ...)` to initialize the random seed. 

- Use `options(pmt_progress = FALSE)` to disable the progress bar. 

    (By default, a progress bar will appear when calculating the permutation distribution if R is used interactively)

- Explore `?PermuTest` (all tests' base class) for all available methods and attributes.

- Check `pmts()` for all available tests. 
    ```{r, pmts}
    pmts()
    ```

## References