---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LearnNonparam

<!-- badges: start -->
[![R-CMD-check](https://github.com/qddyy/LearnNonparam/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/qddyy/LearnNonparam/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of LearnNonparam is to conduct non-parametric tests (mostly based on permutations). 

## Installation

You can install the development version of LearnNonparam from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("qddyy/LearnNonparam", dependencies = TRUE, upgrade = "never")
```

## Example

```{r}
library(LearnNonparam)
```

- Create a test (for example, a `Wilcoxon` object)
    ```{r}
    t <- Wilcoxon$new(type = "permu", n_permu = 10000)
    ```

    or you can use `pmt` (**p**er**m**utation **t**est) function (**Recommended**):
    ```{r}
    # See ?pmt
    t <- pmt("twosample.wilcoxon", type = "permu", n_permu = 10000)
    ```

- feed it the data (`data.frame` | `list` | `vector`)
    ```{r}
    t$feed(Table2.6.2)
    ```

- check the results
    ```{r}
    print(t$statistic)
    print(t$p_value)

    print(t$estimate)
    print(t$ci)

    t$plot_hist(bins = 12)
    ```

- modify some attributes and see how the results change
    ```{r}
    t$type <- "approx"

    print(t$p_value)
    ```

## Help

Just use `?...` syntax. 

If you want to know all available methods and attributes, it's a good idea to explore `?PermuTest` (all tests' **base class**) first. 

If you want to know all available tests, see `pmts()`. 

```{r}
pmts()
```