---
bibliography: man/references/ref.bib
output:
  github_document:
    df_print: kable
    fig_width: 8
    fig_height: 6
    dev: svg
---

```{r, setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE, comment = "#>",
    fig.path = "man/figures/README-", out.width = "100%"
)

library(LearnNonparam)
```

# LearnNonparam <img src="man/figures/logo.svg" alt="logo" width="14%" align="right"/>

[![GPL license](https://img.shields.io/github/license/qddyy/LearnNonparam)](https://cran.r-project.org/web/licenses/GPL-2)
[![GitHub R package version](https://img.shields.io/github/r-package/v/qddyy/LearnNonparam)](https://github.com/qddyy/LearnNonparam)
[![Code size](https://img.shields.io/github/languages/code-size/qddyy/LearnNonparam.svg)](https://github.com/qddyy/LearnNonparam)
[![CodeFactor](https://www.codefactor.io/repository/github/qddyy/LearnNonparam/badge)](https://www.codefactor.io/repository/github/qddyy/LearnNonparam)
[![R CMD check](https://github.com/qddyy/LearnNonparam/workflows/R-CMD-check/badge.svg)](https://github.com/qddyy/LearnNonparam/actions)

## Overview

This package implements some of the non-parametric tests in chapters 1-5 of [@Higgins2003](#references).

Examples in the book can be found [here](https://qddyy.github.io/LearnNonparam/articles/examples). 

## Installation

```{r, install, eval = FALSE}
# install.packages("pak")
pak::pkg_install("qddyy/LearnNonparam")
```

## Usage

- Create a test object (for example, a `Wilcoxon` object)
    ```{r, eval = FALSE}
    t <- Wilcoxon$new(alternative = "two_sided", type = "permu", n_permu = 1e6)
    ```

    or you can use `pmt` (**p**er**m**utation **t**est) function (*Recommended*):
    ```{r, create}
    t <- pmt("twosample.wilcoxon", alternative = "two_sided", type = "permu", n_permu = 1e6)
    ```

- Test some data
    ```{r, test}
    t$test(rnorm(20, 1), rnorm(20, 0))
    ```

- Check the results
    ```{r, results}
    t$p_value

    t$print(digits = 2)

    t$plot(style = "ggplot2", binwidth = 1)
    ```

- Modify some attributes and see how the results change
    ```{r, modify}
    t$type <- "asymp"

    t$p_value
    ```

implemented:

```{r}
pmts()
```

## References