---
bibliography: ref.bib
link-citations: true
output:
  github_document:
    html_preview: false
    dev: svg
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LearnNonparam

<!-- badges: start -->
[![R-CMD-check](https://github.com/qddyy/LearnNonparam/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/qddyy/LearnNonparam/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This package implements the tests in chapters 1-5 of @Higgins2003.

It uses [R6](https://cran.r-project.org/package=R6) for clean OO-design and object property-changes, as well as [arrangements](https://cran.r-project.org/package=arrangements) for fast generation of permutations.

## Installation

You can install the development version of LearnNonparam from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("qddyy/LearnNonparam", dependencies = TRUE)
```

## Usage

```{r}
library(LearnNonparam)
```

- Create a test (for example, a `Wilcoxon` object)
    ```{r}
    t <- Wilcoxon$new(type = "permu", n_permu = 10000)
    ```

    or you can use `pmt` (**p**er**m**utation **t**est) function (*Recommended*):
    ```{r}
    t <- pmt("twosample.wilcoxon", type = "permu", n_permu = 10000)
    ```

- feed it the data (a data.frame, a list, or some numeric vectors)
    ```{r}
    t$feed(Table2.6.2)
    ```

- check the results
    ```{r}
    print(t$statistic)
    print(t$p_value)

    print(t$estimate)
    print(t$ci)

    t$plot_hist(bins = 12)
    ```

- modify some attributes and see how the results change
    ```{r}
    t$type <- "approx"

    print(t$p_value)
    ```

There's also support for chained calls, which means that you can do things like

```{r, eval=FALSE}
pmt("twosample.wilcoxon", type = "permu", n_permu = 10000)$feed(Table2.6.2)$plot_hist(bins = 12)$p_value
```

## Help

Just use `?...` syntax. 

If you want to know all available methods and attributes, it's a good idea to explore `?PermuTest` (all tests' **base class**) first. 

If you want to know all available tests, see `pmts()`. 

```{r}
pmts()
```

## References